---
title: "Data Cleaning and Analysis for JDBP Time-Out Manuscript"
author: "Knight et al."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
```

Start by loading relevant packages and reading in data.

```{r, include=FALSE}

library(tidyverse)
library(haven)
library(knitr)
library(methodsR)
library(rlang)
library(twang)
library(survey)
library(broom)
library(writexl)

set.seed(12345)

tbl <- read_dta("../data/Head Start Data 2-5-15.dta")

tbl <- tbl %>%
  select(B3P_DTO, AAGE, AMOM, DEPRESS2, ENGLISH, HGCG, LANG_GR, MAGE, MRISK3, PREGNANT, PREVPRG, 
         PREVPRGR,	PRIMEOCC, RACE, TEENMOM, ADULTS_G, LIVEARR, MALEHH, MISSCHLD, NCHLD05, NCHLD617, 
         NMOVES,	OWNS, AFDC, AFDCR, FOODST, FOODSTR, MEDICAID, MISSPOV, PUBHSE, POV1, POV2, POV3, 
         POV4, POVLINE, POVRATIO, SSI, SSIR, WIC, WICR, CCARE, FOOD, FOODR, HOUSING, HOUSINGR, 
         MEDICAL, MEDICALR, MONEY, MONEYR, SUPPLIES, SUPPORT, TRANSPRT, TRANSPTR, TEEN_MOM,	
         BL_IDLE, BL_SNGL, BL_WELF, BL_DROP, BL_5CNT, BL_5RSK, BL_3RSK, BL_HRSK,  CSEX, CHLDAGEG, 
         C_MALE, C_MALER, CDOB, CMTHS, EARLYBTH, EARLYR, FRSTBORN, INSUR,	LT2500G, LT2500GR, 
         STAYHOSP, BM_RISKS, CONCERNR, CONCERNS, EN_RISKS, ES_RISKS, EVAL,	EVALR, RISKS, RISKSR, 
         B0P_CESD, B0P_DEP, B0P_CDSF, B0P_DEPS, B5P_ALCH,	B1P_PCDI, B1P_PD, B2P_PCDI, B2P_PD, 
         B3P_PCDI, B3P_PD, B5P_DISP,	B3P_DRST,	B3P_DWRN, B3P_DWRV, B4PSPANK, B3D_CDSF, B2D_CESD, 
         B2D_PCDI,	B2D_PD, B4HM_DATA, B4HMENVN, B5HMEXTE, B5HMINTE, B5HMLCHO, B4HMTOTL,	B5HMVERB, 
         B4HMWARM, B5HMWARM, B5HOMET, B3P_EXPH, B3P_HRSH, B3P_INPH, B3P_WARM, B5PFDATA, B3P_CAR1,	
         B2P_DIS, BVP_FAT1, BVP_FAT6, B2P_HLP2, BVP_LBI1, 	BVP_LBI3, BVP_MAL1, BVP_MAL6, BVP_MBI1, 
         BVP_MBI3, BVP_NLL1,	BVP_NLL3, BVP_NLN3, BVP_NMM1, BVP_NMM3, BVP_NMN3, B3P_SUPP, B3D_SAME,	
         B4CBCLAG, B1P_EEMO, B1P_ESOC, B5CB_AGR,  B5CB_APR, B5CB_AXR, B5CB_EXR, B5CB_INR, B5CB_RBR, 
         B5CB_SCR, B5CB_SPR, B5CB_TPR, B5CB_WDR,	B4FSAGGR, B4FSAPPR, B4FSHYPR, B4FSPROB, B4FSWITH, 
         B5P_ADD, B2P_COMB, B1P_EGE1, B1P_EGES,	B2P_SEN2, B2P_SEN3, B1P_VCO1, B1P_VCOM, B2P_VPR1, 
         B5P_IEP, B5P_RETN, B5P418,	B4PCIEP, B4PSPEECH, B3B_M2FR, B3B_M2FS,	B2B_MLAN, B2B_MVSP, 
         B3RPPVT1, B3RPPVT2, B3RPPVT3, B3RPPVT4,	B3RPPVTS, B3RTVIP2, B3RTVIPS, C4PP_DATA, C4PPVT3S, 
         C5PPVT3S, C5PPVT85, C4TV_DATA,	C4TVIPS, C4_DATA, C4BK_DATA, C4BKCOMP, C4BKKNOW, C4WJ_DATA, 
         C4WJAPSS, C4WJLWSS,	C4WM_DATA, C4WMAPSS, C4WMLISS, C5_DATA, C5MATHRA, C5MRSS, C5RDSIRT, 
         C4LA_DATA, C4LASADC,	C4LASLL, C4LASLLC, C4LASLR, C4LASLRC, C4LASUL, C4LASULC, C4LASUR, 
         C4LASURC, C4LCOGNS,	C4LEMORS, C4LT_DATA, C4LTRACT, C4LTRANX, C4LTRASC, C4LTRASE, C4LTRATT, 
         C4LTRFEL, C4LTRORG,	C4LTRREG, C4LTRSEN, C4LTRSOC, C5_BULLY, C5_DELB, C5_FREL, C5_MREL, 
         C5_MTR, C5C_ANGR,  C5C_PEER, C5C_SAD, C5S_DATA, C5RISK16, C5RISK3, C5RISK4, C5RSK3EQ, C5RSK3NE, 
         C5RSKACD,	C5RSKHEI, C5RSKML, C5RSKPPM, C5RSKRTN ,C5RSKSC1, C5RSKSC2, C5RSKSC3, C5SCHEXP4, 
         C5SUCABR,  C5SUCACD, C5SUCCES, C5SUCCES2, C5SUCPPM, C5SUCSOC, C5WT_CA_PI, C5WT_CA, B5VCPOS, 
         B5VCNEG, B5P_EDUC, B3P_DTAC, B3D_DTAC, P2V2_ANY, B3P_CDSF, B4PCESD, B5P_CESD, B5P_SUBS, 
         B5P_ALCH,	T4CORCRE, T5_SSRS_SC, B5P_DATA, C5WT_CA_PI, POV1, POV2, POV3, POV4, POVLINE, POVRATIO, MISSCIRC,
         B3V3CENG, B3V3CNEG, B3V3PDET, B3P_DPRV, B3P_DPH1, B3P_DRMV, B3P_DRST, B3P_DSHO, B3P_DTHR, B3P_DTLK, B3P_DWRN, B3P_DWRV, 
         B4PDPDET, BPDPNET, B4PDCENG, T4CISDET) %>%  
  zap_labels()

```

A few variable recodes. 

- Log income ratio
- Dummy variable for "Uses Physical Violence"
- Reverse code "Relationship with Father"
- Create labeled factors, as necessary

Also, filter to cases with grade 5 time out data only.

```{r}

tbl <- tbl %>%
  mutate(INCOMERATIO = log(POVRATIO+.01),
         PHYS        = as.numeric(B3P_DTAC == 5),
         rev_C5_FREL = 4 - C5_FREL) %>% 
  mutate(TEENMOM   = factor(TEENMOM, levels = 0:1, labels = c("Not Teen Mother", "Teen Mother")),
         P2V2_ANY  = factor(P2V2_ANY, levels = 0:1, labels = c("No Services", "Received Services")),
         B5P_SUBS  = factor(B5P_SUBS, levels = 0:1, labels = c("No SA", "Substance Abuse")),
         RACE      = factor(RACE, levels = 1:4, labels = c("White", "Af Am", "Hispanic", "Other")),
         B3P_DTO   = factor(B3P_DTO, levels = 0:1, labels = c("No TO", "Used TO"))) %>% 
  mutate(B3P_DPRV  = factor(B3P_DPRV, levels = 0:1, labels = c("No Prev", "Prevent/Distract")),
         B3P_DRMV = factor(B3P_DRMV, levels = 0:1, labels = c("No Removal", "Discipline: Remove Child/Object")),
         B3P_DRST = factor(B3P_DRST, levels = 0:1, labels = c("No Restraint", "Discipline: Restrain")),
         B3P_DSHO = factor(B3P_DSHO, levels = 0:1, labels = c("No Shouting", "Discipline: Shout")),
         B3P_DTHR = factor(B3P_DTHR, levels = 0:1, labels = c("No Threaten", "Discipline: Threaten")),
         B3P_DTLK = factor(B3P_DTLK, levels = 0:1, labels = c("No Explanation", "Talk/Explain")),
         B3P_DWRN = factor(B3P_DWRN, levels = 0:1, labels = c("No Non-Verbal Warning", "Discipline: Warn/Remind (Non-Verbal)")),
         B3P_DWRV = factor(B3P_DWRV, levels = 0:1, labels = c("No Verbal Warning", "Discipline: Warn/Remind (Verbal)"))) %>%
  filter(B5P_DATA==1 & !is.na(B3P_DTO))

```

Declare variables and their role.

```{r}

dvs_36m  <- c("B3V3CENG",   # Child Engagment of Parent (3-bag)
              "B3V3CNEG",   # Child Negativity Towards Parent (3-bag),
              "B3V3PDET"    # Detachment (3-bag)
              )

dvs_prek <- c("T4CORCRE",   # Creative Representation (Pre-K)
              "B4CBCLAG",   # CBCL Aggressive Behavior
              "T4CISDET",   # Arnett Caregiver Interaction Scale detachment
              "B4PDPDET",   # Detachment (Play-doh)
              "BPDPNET",    # Negative Regard (Play-doh)
              "B4PDCENG"    # Child Engagement (Play-doh)
              )

dvs_g5 <- c("B5VCPOS",    # Positivity toward Parent
         "B5VCNEG",       # Negativity toward Parent
         "B5CB_AXR",      # Anxious/Depressed Raw Score
         "B5CB_RBR",      # Rule-Breaking Behavior Raw Score
         "B5CB_AGR",      # Aggressive Behavior Raw Score
         "B5CB_INR",      # Internalizing Raw Score
         "B5CB_EXR",      # Externalizing Raw Score
         "C5_FREL",       # Relationship with Dad
         "C5_MREL",       # Relationship with Mom
         "T5_SSRS_SC"     # Self-Control
         )

controls <- c("TEENMOM",     # Teen Mother",
              "B5P_EDUC",    # Mother Education",
              "P2V2_ANY",    # Receives Services",
              "B3P_CDSF",    # Depression (36 months)",
              "B5P_SUBS",    # Substance Abuse",
              "B5P_ALCH",    # Level of Alcohol Abuse",
              "INCOMERATIO", # "Income/Poverty Ratio (Log)",
              "RACE",        # Primary caregiver's race,
              "B3P_DPRV",    # Discipline: Prevent/Distract
              "B3P_DRMV",    # Discipline: Remove Child/Object
              "B3P_DRST",    # Discipline: Restrain
              "B3P_DSHO",    # Discipline: Shout
              "B3P_DTHR",    # Discipline: Threaten
              "B3P_DTLK",    # Discipline: Talk/Explain
              "B3P_DWRN",    # Discipline: Warn/Remind (Non-Verbal)
              "B3P_DWRV",    # Discipline: Warn/Remind (Verbal)
              "B3P_DPH1"     # Discipline: Physical Punishment
              )

tx <- "B3P_DTO" 


```

The discipline variables are based on the following description from the codebook:

> Discipline Strategies--measures the parent's strategies for handling four different potential conflict situations with the
child: 1) the child keeps playing with breakable things; 2) the child refuses to eat; 3) the child throws a temper tantrum in a public place
4) the child hits the parent in anger (# 4 is only available at 36-Months). Parents provided open-ended answers to how they would respond
to each of the four situations, and these responses were classified into the types of discipline strategies, which were coded as binary
variables. A parent received a "1" for each strategy that was ever mentioned.

The following are sample responses for each type of discipline:

- Prevent/Distract: If parent responded "put things out of reach/distract child with activity/make new food/play a game to get him/her to eat/ give child food/ distract child/give child something to play with/hold child/hold child's hand until child is calm" in any one of the 3 or 4 scenarios then BnP_DPRV is set equal to 1.
- Threaten: If parent responded "leave and expect child to follow/tell child parent will punish him/her at home" in any one of the 3 or 4 scenarios then BnP_DTHR is set equal to 1.
- Shout: If parent responded "shout at child/punish child verbally/yell at child" in any one of the 3 or 4 scenarios then BnP_DSHO is set equal to 1.
- Talk/Explain: If parent responded "tell child NO and explain why/ask child to put object down/explain importance of eating/continue to try to get child to eat, but don't force child/ talk to child" in any one of the 3 or 4 scenarios then BnP_DTLK is set equal to 1.
- Remove Child/Object: If parent responded "take child away/stop feeding child; child is not hungry/take food away/pick up child and leave" in any one of the 3 or 4 scenarios then BnP_DRMV is set equal to 1.
- Restrain: If parent responded to restrain child in any one of the 4 scenarios then B3P_DRST is set equal to 1.
- Time Out: If parent responded "give child time out or quiet time/child must sit in corner" in any one of the 4 scenarios then BnP_DTO is set equal to 1.
- Shout: If parent responded "shout at child/punish child verbally/yell at child" in any one of the 3 or 4 scenarios then BnP_DSHO is set equal to 1.
- Warn/Remind (Verbal): If parent responded "threaten to take away treats/threaten time out when get home" in any one of the 4 scenarios then B3P_DWRV is set equal to 1. 
- Warn/Remind (Non-Verbal): If parent responded "Tell child no and expect child to obey/ count/the "look"/stare at child" in any one of the 4 scenarios then B3P_DWRN is set equal to 1.

Create a function to create cleaner tables.

```{r}

var_labs <- function(tbl, var){
  
  var <- sym(var)
  
  tbl %>%
    mutate(!!var := case_when(
      !!var == "B3V3CENG"     ~ "36 mo.: Child Engagment of Parent",
      !!var == "B3V3CNEG"     ~ "36 mo.: Child Negativity Towards Parent",
      !!var == "B3V3PDET"     ~ "36 mo.: Detachment",
      !!var == "T4CORCRE"     ~ "Pre-K: Creative Representation",
      !!var == "B4CBCLAG"     ~ "Pre-K: CBCL Aggressive Behavior",
      !!var == "T4CISDET"     ~ "Pre-K: Arnett Caregiver Interaction Scale detachment",
      !!var == "B4PDPDET"     ~ "Pre-K: Detachment",
      !!var == "BPDPNET"      ~ "Pre-K: Negative Regard",
      !!var == "B4PDCENG"     ~ "Pre-K: Child Engagement",
      !!var == "B5VCPOS"      ~ "Grade 5: Positivity toward Parent",
      !!var == "B5VCNEG"      ~ "Grade 5: Negativity toward Parent",
      !!var == "B5CB_AXR"     ~ "Grade 5: Anxious/Depressed Raw Score",
      !!var == "B3P_WARM"     ~ "Grade 5: HOMES Parental Warmth",
      !!var == "B5CB_RBR"     ~ "Grade 5: Rule-Breaking Behavior Raw Score",
      !!var == "B5CB_AGR"     ~ "Grade 5: Aggressive Behavior Raw Score",
      !!var == "B5CB_INR"     ~ "Grade 5: Internalizing Raw Score",
      !!var == "B5CB_EXR"     ~ "Grade 5: Externalizing Raw Score",
      !!var == "C5_DELB"      ~ "Grade 5: Delinquent Behaviors",
      !!var == "C5_FREL"      ~ "Grade 5: Relationship with Dad",
      !!var == "C5_MREL"      ~ "Grade 5: Relationship with Mom",
      !!var == "T5_SSRS_SC"   ~ "Grade 5: Self-Control",
      !!var == "TEENMOM"      ~ "Teen Mother (Baseline Survey)",
      !!var == "B5P_EDUC"     ~ "Grade 5: Mother Education",
      !!var == "P2V2_ANY"     ~ "Receives Services (Any Study Year)",
      !!var == "B3P_CDSF"     ~ "36 mo.: Depression",
      !!var == "B5P_SUBS"     ~ "Grade 5: Substance Abuse",
      !!var == "B5P_ALCH"     ~ "Grade 5: Level of Alcohol Abuse",
      !!var == "INCOMERATIO"  ~ "Income/Poverty Ratio (Log) (Baseline Survey)",
      !!var == "RACE"         ~ "Primary Caregiver's Race (Baseline Survey)",
      !!var == "B3P_DPRV"     ~ "36 mo.: Discipline - Prevent/Distract",
      !!var == "B3P_DRMV"     ~ "36 mo.: Discipline - Remove Child/Object",
      !!var == "B3P_DRST"     ~ "36 mo.: Discipline - Restrain",
      !!var == "B3P_DSHO"     ~ "36 mo.: Discipline - Shout",
      !!var == "B3P_DTHR"     ~ "36 mo.: Discipline - Threaten",
      !!var == "B3P_DTLK"     ~ "36 mo.: Discipline - Talk/Explain",
      !!var == "B3P_DWRN"     ~ "36 mo.: Discipline - Warn/Remind (Non-Verbal)",
      !!var == "B3P_DWRV"     ~ "36 mo.: Discipline - Warn/Remind (Verbal)",
      !!var == "B3P_DPH1"     ~ "36 mo.: Discipline - Physical Punishment",
      !!var == "B3P_DTOUsed TO"            ~ "Used Time-Out",
      !!var == "TEENMOMTeen Mother"        ~ "Teen Mother",
      !!var == "P2V2_ANYReceived Services" ~ "Received Services (Any Study Year)",
      !!var == "B5P_SUBSSubstance Abuse"   ~ "Grade 5: Parent Substance Abuse",
      !!var == "RACEAf Am"                 ~ "African American",
      !!var == "RACEHispanic"              ~ "Hispanic",
      !!var == "RACEOther"                 ~ "Other Race",
      !!var == "B3P_DPRVPrevent/Distract"  ~ "36 mo.: Discipline - Prevent/Distract",
      !!var == "B3P_DRMVDiscipline: Remove Child/Object"       ~ "36 mo.: Discipline - Remove Child/Object",
      !!var == "B3P_DRSTDiscipline: Restrain"                  ~ "36 mo.: Discipline - Restrain",
      !!var == "B3P_DSHODiscipline: Shout"                     ~ "36 mo.: Discipline - Shout",
      !!var == "B3P_DTHRDiscipline: Threaten"                  ~ "36 mo.: Discipline - Threaten",
      !!var == "B3P_DTLKTalk/Explain"                          ~ "36 mo.: Discipline - Talk/Explain",
      !!var == "B3P_DWRNDiscipline: Warn/Remind (Non-Verbal)"  ~ "36 mo.: Discipline - Warn/Remind (Non-Verbal)",
      !!var == "B3P_DWRVDiscipline: Warn/Remind (Verbal)"      ~ "36 mo.: Discipline - Warn/Remind (Verbal)",
      TRUE ~ !!var))

}

```


## Descriptive Statistics

First, Table 1 (Controls)

```{r}

tbl_controls <- tbl %>%
  summary_all(variables = controls) %>%
  var_labs("Variable")

tbl_controls_tx <- tbl %>%
  summary_all(treatment = tx, variables = controls) %>%
  var_labs("Variable")

tbl_controls_mw <- tbl %>%
  summary_all(treatment = tx, variables = controls, cont_function = summary_median_IQR) %>%
  filter(nchar(`No TO (N=998)`) > 0 & nchar(`P Value`) > 0) %>%
  var_labs("Variable") %>%
  dplyr::select(Variable, `Mann-Whitney p` = `P Value`)
  
control_tbl <- tbl_controls %>%
  left_join(tbl_controls_tx, by = c("Variable", "Label")) %>%
  left_join(tbl_controls_mw, by = "Variable") %>%
  mutate(`Mann-Whitney p` = ifelse(is.na(`Mann-Whitney p`), "", `Mann-Whitney p`)) %>%
  dplyr::rename(`All Cases` = Statistics)

kable(control_tbl)

```

36 Month Outcomes.

```{r}

tbl_36m  <- tbl %>%
  summary_all(variables = dvs_36m) %>%
  var_labs("Variable")

tbl__36m_tx  <- tbl %>%
  summary_all(treatment = tx, variables = dvs_36m) %>%
  var_labs("Variable")

tbl_36m_mw <- tbl %>%
  summary_all(treatment = tx, variables = dvs_36m, cont_function = summary_median_IQR) %>%
  filter(nchar(`No TO (N=998)`) > 0 & nchar(`P Value`) > 0) %>%
  var_labs("Variable") %>%
  dplyr::select(Variable, `Mann-Whitney p` = `P Value`)


dv_36m_tbl <- tbl_36m %>%
  left_join(tbl__36m_tx, by = c("Variable"))  %>%
  left_join(tbl_36m_mw, by = "Variable") %>%
  mutate(`Mann-Whitney p` = ifelse(is.na(`Mann-Whitney p`), "", `Mann-Whitney p`)) %>%
  dplyr::rename(`All Cases` = `Mean (SD)`)

kable(dv_36m_tbl)

```

Pre-K.

```{r}

tbl_prek  <- tbl %>%
  summary_all(variables = dvs_prek) %>%
  var_labs("Variable")

tbl_prek_tx  <- tbl %>%
  summary_all(treatment = tx, variables = dvs_prek) %>%
  var_labs("Variable")

tbl_prek_mw <- tbl %>%
  summary_all(treatment = tx, variables = dvs_prek, cont_function = summary_median_IQR) %>%
  filter(nchar(`No TO (N=998)`) > 0 & nchar(`P Value`) > 0) %>%
  var_labs("Variable") %>%
  dplyr::select(Variable, `Mann-Whitney p` = `P Value`)


dv_prek_tbl <- tbl_prek %>%
  left_join(tbl_prek_tx, by = c("Variable"))  %>%
  left_join(tbl_prek_mw, by = "Variable") %>%
  mutate(`Mann-Whitney p` = ifelse(is.na(`Mann-Whitney p`), "", `Mann-Whitney p`)) %>%
  dplyr::rename(`All Cases` = `Mean (SD)`)

kable(dv_prek_tbl)

```

Grade 5.

```{r}

tbl_g5  <- tbl %>%
  summary_all(variables = dvs_g5) %>%
  var_labs("Variable")

tbl_g5_tx  <- tbl %>%
  summary_all(treatment = tx, variables = dvs_g5) %>%
  var_labs("Variable")


tbl_g5_mw <- tbl %>%
  summary_all(treatment = tx, variables = dvs_g5, cont_function = summary_median_IQR) %>%
  filter(nchar(`No TO (N=998)`) > 0 & nchar(`P Value`) > 0) %>%
  var_labs("Variable") %>%
  dplyr::select(Variable, `Mann-Whitney p` = `P Value`)


dv_g5_tbl <- tbl_g5 %>%
  left_join(tbl_g5_tx, by = c("Variable"))  %>%
  left_join(tbl_g5_mw, by = "Variable") %>%
  mutate(`Mann-Whitney p` = ifelse(is.na(`Mann-Whitney p`), "", `Mann-Whitney p`)) %>%
  dplyr::rename(`All Cases` = `Mean (SD)`)

kable(dv_g5_tbl)

```

## Graphical Display

Get boxplots.

```{r}

tbl_long <- tbl %>%
  select(tx, dvs_36m, dvs_prek, dvs_g5) %>%
  gather(Variable, Value, B3V3CENG:T5_SSRS_SC) %>%
  var_labs("Variable") %>%
  mutate(Variable = as.factor(Variable)) %>%
  mutate(Variable = fct_relevel(Variable, "36 mo.: Child Engagment of Parent",
                                                     "36 mo.: Child Negativity Towards Parent",
                                                     "36 mo.: Detachment",
                                                     "Pre-K: Arnett Caregiver Interaction Scale detachment",
                                                     "Pre-K: CBCL Aggressive Behavior",
                                                     "Pre-K: Child Engagement",
                                                     "Pre-K: Creative Representation",
                                                     "Pre-K: Detachment",
                                                     "Pre-K: Negative Regard",
                                                     "Grade 5: Aggressive Behavior Raw Score",
                                                     "Grade 5: Anxious/Depressed Raw Score",
                                                     "Grade 5: Delinquent Behaviors",
                                                     "Grade 5: Externalizing Raw Score",
                                                     "Grade 5: Internalizing Raw Score",
                                                     "Grade 5: Negativity toward Parent",
                                                     "Grade 5: Positivity toward Parent",
                                                     "Grade 5: Relationship with Dad",
                                                     "Grade 5: Relationship with Mom",
                                                     "Grade 5: Rule-Breaking Behavior Raw Score",
                                                     "Grade 5: Self-Control"))

tbl_long %>%
  ggplot(aes(x = B3P_DTO, y = Value)) + geom_boxplot(fill = "firebrick") + 
  facet_wrap(~Variable, ncol = 4, scale = "free_y") +
  labs(x = "")

```


## Log Transforms

Most of the outcomes are skewed, so they are log transformed.  Mother and Father relationships at grade 5 have a negative skew, so they are reverse-coded first.

```{r}

tbl <- tbl %>%
  mutate(C5_FREL = 4 - C5_FREL,
         C5_MREL = 4 - C5_MREL) %>%
  mutate_at(c(dvs_36m, dvs_prek, dvs_g5), ~log(.+.01))



```


## PS Weighting

Drop missing values.

```{r}

tbl2match <- tbl %>%
  select(tx, controls, dvs_36m, dvs_prek, dvs_g5) %>% 
  na.omit() %>%
  mutate(B3P_DTO = as.numeric(B3P_DTO == "Used TO"))
  
```

Get PS weights.

```{r}

tbl <- tbl %>%
  mutate(num_to = as.numeric(B3P_DTO == "Used TO")) %>%
  as.data.frame()

ps_out <- ps(as.formula(paste("num_to", "~", paste(controls, collapse = " + "))),
                     data = tbl,
             interaction.depth=2,
            estimand = "ATE",
               verbose = F,
               stop.method = "ks.mean",
               n.trees = 2000)

plot(ps_out)

```

Review balance.

```{r}

summary(ps_out)

plot(ps_out, plots = 3)

```

Declare weights.

```{r}

tbl <- tbl %>%
  mutate(wt = get.weights(ps_out, stop.method = "ks.mean"))

design_ps <- svydesign(ids = ~1, weights = ~ wt, data = tbl)

```

Get ATEs.

```{r}

get_ate <- function(dv, tx, dsn) {
  
  form <- formula(paste(dv,"~", tx))
  
  svyglm(form, design = dsn) %>%
    tidy %>%
    filter(term != "(Intercept)") %>%
    mutate(Variable = dv) %>%
    mutate_if(is.numeric, ~round(., 3))  %>%
    mutate(p = if_else(p.value < .001, "< 0.001", as.character(p.value))) %>%
    dplyr::select(Variable, term, ATE = estimate, SE = std.error, t = statistic, p)
  
}


ates <- map_df(c(dvs_36m, dvs_prek, dvs_g5), ~get_ate(.x, tx = "B3P_DTO", dsn = design_ps)) %>%
  var_labs("Variable") %>%
  dplyr::select(-term) 

kable(ates, align = c("l", rep("c",4)))

```


## Regression

Write function to clean regression results.

```{r}


get_reg <- function(dv, tx, controls) {
  
  form <- formula(paste(dv,"~", paste(c(tx, controls), collapse = " + ")))
  
  lm(form, data = tbl) %>%
    tidy %>%
    filter(term == "B3P_DTOUsed TO") %>%
    mutate(Variable = dv) %>%
    mutate_if(is.numeric, ~round(., 3))  %>%
    mutate(p = if_else(p.value < .001, "< 0.001", as.character(p.value))) %>%
    dplyr::select(Variable, term, B = estimate, SE = std.error, t = statistic, p)
  
}


```

Map over outcomes.

```{r}

regs <- map_df(c(dvs_36m, dvs_prek, dvs_g5), ~get_reg(.x, tx = "B3P_DTO", controls = controls)) %>%
  var_labs("Variable") %>%
  dplyr::select(-term)

kable(regs)

```

Present the full regression results for reference.

```{r}

get_full_reg <- function(dv, tx, controls) {
  
  dv   <- sym(dv)
  
  form <- formula(paste(dv,"~", paste(c(tx, controls), collapse = " + ")))
  
  lm(form, data = tbl) %>%
    tidy %>%
    mutate_if(is.numeric, ~round(., 3))  %>%
    mutate(!!dv := case_when(
      p.value < 0.001 ~ paste0(estimate, "***", " (", std.error, ")"),
      p.value < 0.01  ~ paste0(estimate, "**", " (", std.error, ")"),
      p.value < 0.05  ~ paste0(estimate, "*", " (", std.error, ")"),
      TRUE            ~ paste0(estimate, " (", std.error, ")")
    )) %>%
    select(Term = term, !!dv)

}


full_regs <- map(c(dvs_36m, dvs_prek, dvs_g5), ~get_full_reg(.x, tx = "B3P_DTO", controls = controls)) %>%
  reduce(full_join, by = "Term") %>%
  gather(Variable, Value, B3V3CENG:T5_SSRS_SC) %>%
  var_labs("Variable") %>%
  spread(Variable, Value) %>%
  var_labs("Term")

kable(full_regs)

```

## Write out tables

```{r}

write_xlsx(list(`Control Desc` = control_tbl,
           `36m Desc`     = dv_36m_tbl,
           `Pre-K Desc`   = dv_prek_tbl,
           `G5 Desc`      = dv_g5_tbl,
           `ATEs`         = ates,
           `Regressions`  = regs),
           path = "tables.xlsx")

```
